---
title: "Shitty introduction to R"
author: "Elias M. Guerra"
date: "5/18/2018"
output: github_document
---

This is not a guide on how to code in R. It’s just how I do it. I don’t explain everything that I’m doing. You can figure it out. 

Onward. 


```{r echo=FALSE, fig.height=6, message=FALSE, warning=FALSE, paged.print=FALSE}
## install.packages("imager") ## I've already done this before so I don't need to do it again
library(imager)
im <- load.image("machine_learning.png")
plot(im, axes = F)

```

I had to look at the following pages to figure out how to include the above picture:

1. https://dahtah.github.io/imager/imager.html

2. https://stackoverflow.com/questions/26881866/resizing-images-in-rmarkdown 

Comic from: https://xkcd.com/1838/ 

Next.

There are lots of different terms for all the computer stuff that you use in R like vectors, booleans, factors, concatenate, for loops, if else statements, decision trees, etc. I don't know all the names. I don't think it's that big a deal. 

### R works like this:

```{r}
x <- 1
y <- 2
# This is a comment
z = 3 # Some people say you shouldn't use the equals sign idk 
x
## x <- 100
x + y + z
y^2
y1 <- c(1,2,3,4,5)
x1 <- seq(from = 1, to = 212, length = 5)
x1
plot(x1, y1)


df1 <- data.frame(v1 = rnorm(n = 10, mean = -20, sd = 4),
                  v2 = runif(n = 10, min = -20, max = 212))
?rnorm # Draw n random values from the normal distribution 
?runif # Draw n random value from uniform distribution
df1
str(df1) # This is better than printing a huge data frame
df1$v1
df1$v1[1]
df1[1,1]
df1[1:5,]
df1$v2 > 100 
true.false <- df1$v2 > 100
df1[true.false,]
df1$v1[true.false]
```

This is all just one big logic problem. 

### This is a big one:

This is a for loop. 

```{r}
for (i in 1:5) {
  print(i)
}

n <- 5 # This line is useful
xx <- seq(1,100,length = n)
for (i in 1:n) {
  aa <- xx[i]
  print(aa) ## I could also have written print(xx[i])
}
## Take a look at xx if this does not make sense
```

You can do a lot with for loops. Below is just an example. 

I'm using this dataset from the ggplot2 package about 38 popular car models in 1999 and 2008. I want to know the average miles per gallon (on the highway) for each manufacturer in 1999 and 2008. 
 
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
## install.packages("ggplot2")
## You'll need to uncomment the above line if you want to run this yourself
library(ggplot2)
library(knitr)
str(mpg)
mpg.hwy <- matrix(ncol = 3, nrow = 0)
for (y in unique(mpg$year)) {
  for (m in unique(mpg$manufacturer)) {
    mm <- mpg[mpg$year == y & mpg$manufacturer == m, ]
    ifelse(nrow(mm) == 0, h <- NA, h <- mean(mm$hwy))
    new.row <- c(yr = y, man = m, hwy = h)
    mpg.hwy <- rbind(mpg.hwy, new.row)
  }
}
data.frame(mpg.hwy)
qplot(data = data.frame(mpg.hwy), 
      geom = "tile", 
      x = yr, y = man, fill= as.numeric(hwy),
      xlab = NULL, ylab = NULL) + 
  labs(fill = "MPG on highway") 
```

### Here are some basic statistics tools:

```{r}
lm1 <- lm(data = df1, v2 ~ v1)
# lm(df1$v1 ~ df1$v2)   ## This would also work
?lm # Fit a linear model to your data 
plot(data = df1, v2 ~ v1)
abline(lm1)

rr.m <- NULL # See what happens when you leave this step out
for (i in 1:10000) {
  rr <- rexp(100, rate = 4)
  rr.m[i] <- mean(rr)
}
hist(rr.m, breaks = 100)
plot(rr.m)
```

Those are most of the basics. 

Other things:

* Functions: I've really been trying to write more of the long code I do as functions. This means I don't have to copy and paste it elsewhere. 